Bayesian model in JAGS

### 2023-01-26 4_RSV_disease_burden/4_RSV_disease_burden.Rmd
delte output html

---
title: "Estimate RSV disease burden using hierarchical baysian regression"
author: "ZHE ZHENG"
date: "2023-01-26"
output: html_document
---

@@

>>>>

---
title: "Bayesian model in JAGS"
subtitle: "Tutorial 3 for transition"
author: "Zhe Zheng (Gigi)^[zhe.zheng@yale.edu]"
date: "2023-01-16"
fontsize: 10pt
output: 
  beamer_presentation:
  theme: CambridgeUS
  colortheme: "beaver"
  fonttheme: "structurebold"
---

@@

- Section 1: Background knowledge of estimating disease burden (hospitalizations/mortality etc) with statistical models.
\
\
- Section 2: Background knowledge of Hierarchical Bayesian regression.
\
\
- Section 3: R code for running the Hierarchical Bayesian regression to estimate in older adults by age and risk groups.
